\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-04-24 chapters/1_intro.tex
Updates to intro and algorithm

\begin{itemize}
\item \textbf{General intro about CNN:} big success in pixel-level image understanding tasks: boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, semantic segmentation \cite{long2015fully,chen2018deeplab,kong2018recurrent}, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet}, pose estimation \cite{wei2016convolutional,cao2017realtime}...
% \SOURCE{\cite{kong2018recurrent}}
\item Many recent successful methods generate \textbf{region proposals} and classify the objects in the bounding box \cite{yang2012layered,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible,he2017mask}
\item \emph{Why we do not like them}:
\begin{itemize}
\item rely on the object detector and non-maximum suppression heuristics to accurately “count” nb. of instances, 
\item underperform in cluttered scenes (assignment carried out independently for each detection) 
\item not usable for wiry or articulated segments/objects 
\item nothing in the architecture preventing a pixel to be shared between two instances
\item number of instances is limited by nb. proposals processed by CNN (usually hundreds). 
\item (difficult to train in an end-to-end manner: interface between instance segmentation and detection is non-differentiable)
% \item (architecture is complex and hard to tune and “debug”...?)
\end{itemize}

\item Among successful \textbf{proposal-free methods} there are: predict pixel embedding vectors \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic}; predict short- and long-range affinities \cite{liu2018affinity,wolf2018mutex,xie2015holistically} (more details in related work)

\item In both approaches we can obtain the final segmentation by using a \textbf{graph clustering algorithm}
\item Recent work (\cite{wolf2018mutex}, more...) shows that it is better to use \textbf{repulsion and attraction} (directly predict it with the classifier, no need to define seeds or to fix a threshold given an hierarchy of clusters)
\item solving correlation clustering problem (multicut) is too expensive for this application (even using recently proposed heuristics)
\item our contributions:
\begin{itemize}
\item we propose a unified and simple formalization of Agglomerative Clustering and show how many of the recently proposed methods can be seen as special cases (focusing in particular on signed graphs) (\textbf{review and comparison paper})
\item new clustering algorithms on signed graphs
\item we compare different types of agglomeration clustering on a pixel grid graph with short and long-range connections, focusing on aspects like efficieny, robustness (and MC energy)

>>>>

Deep convolutional neural nets (CNNs) has been successfully applied to a wide range of tasks of computer vision and pixel-level image understanding, such as \UPDATE{boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, semantic segmentation \cite{long2015fully,chen2018deeplab,kong2018recurrent}, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet}, and pose estimation \cite{wei2016convolutional,cao2017realtime}.}

\begin{itemize}
% \SOURCE{\cite{kong2018recurrent}}
\item \emph{Instance segmentation} is a task of computer vision that involves the detection of all objects in an image by performing pixel-level segmentation of each instance.   
\item Many recent successful methods for instance segmentation %, usually named \emph{proposal-based methods}, 
 use heuristic approaches that start from the classical computer vision task of \emph{object detection}, where the goal is to localize each objects using a bounding box, and then predict both a pixel-level mask of each instance and a semantic label (classify the objects in the bounding box). \TODO{Is it really general enough as a description...?} \cite{yang2012layered,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible,he2017mask}
\item While effective, these approaches are \UPDATE{somewhat unsatisfying (copy/paste, change: present some faults)} because:
\begin{itemize}
\item they rely on the object detector and non-maximum suppression heuristics to count how many instances are present in the image, 
\item they tend to underperform in cluttered scenes, since instance assignment is often carried out independently for each detection; 
\item they are not usable for wiry or articulated objects (e.g. in the field of connectomics and neuron segmenation from electron microscopy images) 
\item their architecture do not usually prevent a pixel to be shared between multiple instances
\item they do not scale up well since each proposal has to be singularly processed by the CNN. 
% \item (difficult to train in an end-to-end manner: interface between instance segmentation and detection is non-differentiable)
% \item (architecture is complex and hard to tune and “debug”...?)
\end{itemize}

\item Currently there are two successful approaches used for proposal-free instance segmentation: the first ones predict associative pixel embedding vectors, where the goal is to have a CNN predicting embedding vectors that are similar only for pixels in the same instance \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic}; in the second type of approaches, for every pixel a set of neighboring pixels is fixed  (not necesarelly limited to the direct neighbors) and a CNN then predicts affinities, that represent how likelity it is for each of neighboring pixels to be in the same instance \cite{liu2018affinity,wolf2018mutex,xie2015holistically}

\item Both approaches requires a final clustering algorithm to output the final instance segmentation

 and we can define a grid graph, where each vertex represents a pixel, with short- and long-range edge connections

 and find the final instance segmentation by using a graph clustering algorithm.

\item Recent work (\cite{wolf2018mutex}, more...) shows that it is better to use \textbf{repulsion and attraction} (directly predict it with the classifier, no need to define seeds or to fix a threshold given an hierarchy of clusters)
\item solving correlation clustering problem (multicut) is too expensive for this application (even using recently proposed heuristics)
\item our contributions:
\begin{itemize}
\item we propose a unified and simple formalization of Agglomerative Clustering and show how many of the recently proposed methods can be seen as special cases (focusing in particular on signed graphs) (\textbf{review and comparison paper})
\item new clustering algorithms on signed graphs
\item we compare different types of agglomeration clustering on a pixel grid graph with short and long-range connections, focusing on aspects like efficieny, robustness (and MC energy)

### 2019-04-24 chapters/2_rel_work.tex
Update list of update rules and associated algs.
Update NeurIPS style
Updates to intro and algorithm

\section{Related work}
\begin{itemize}
\item \textbf{Proposal based methods} 
\begin{itemize}
\item Generate region proposals or bounding boxes and classify the objects in the bounding box \cite{yang2012layered,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible,he2017mask}; fully convolutional  box proposals \cite{li2017fully}. 
\item \emph{More references:} use an object detector to enumerate candidate instances and then perform pixel-level segmentation of each instance \cite{liang2018proposal,dai2016instance,li2017fully,liang2016reversible,arnab2017pixelwise} or generate generic proposal segments and then label each one with a semantic detector \cite{hariharan2014simultaneous,chen2015multi,hariharan2015hypercolumns,dai2015convolutional,uhrig2016pixel,he2017mask}.
% \SOURCE{\cite{kong2018recurrent}
\end{itemize}

\item \textbf{Proposal-free methods:} 
\begin{itemize}
\item box-free \cite{pinheiro2015learning,pinheiro2016learning,hu2017fastmask}; joint segmentation and instance labeling in a combinatorial framework \cite{kirillov2017instancecut}; recurrent models \cite{romera2016recurrent,ren2017end}; encode instance relationships to classes and exploit the boundary information  \cite{jin2016object}; sequential framework to gradually group from points to lines and then instances \cite{liu2017sgn}
\item \textbf{Pixel embedding vectors}: 
\begin{itemize}
\item supervised vectors \cite{bai2017deep}, unsupervised vectors  \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic} of which \cite{kong2018recurrent} is trained end-to-end;  using scene depth information \cite{uhrig2016pixel}, \TODO{check \cite{sironi2014multiscale}} 
%    \TODO{more on pose estimation, vector distance transform, deep coloring?, ECCV semi-convolutions}

@@

\item \textbf{Graph clustering related work}:
\begin{itemize}
    \item popular in image segmentation: \textbf{agglomerative clustering}.
    \item Why: more efficient than divisive approaches and graph cuts; does not usually require to specify the final number of clusters (e.g. spectral clustering) or seed nodes (e.g. watershed, random walker) 
    % old graph cut paper: \cite{shi2000normalized}
    % \item \emph{[other clustering methods working in an euclidean embedding space like mean-shift, K-means, Mixture models, BIRCH... can most probably be omitted]}
    \item many segmentation pipelines used to start the agglomeration from superpixels (SLIC, \cite{felzenszwalb2004efficient}, watershed) to reduce size of the problem 
    \item usually we build an hierarchy of clusters (or a \emph{merge-tree}): \TODO{find meaningful order}

>>>>

\section{Related work}
\begin{itemize}
\item \textbf{Proposal based methods} 
\begin{itemize}
\item Generate region proposals or bounding boxes and classify the objects in the bounding box \cite{yang2012layered,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible,he2017mask}; fully convolutional  box proposals \cite{li2017fully}. 
\item \emph{More references:} or generate generic proposal segments and then label each one with a semantic detector \cite{hariharan2014simultaneous,chen2015multi,hariharan2015hypercolumns,dai2015convolutional,uhrig2016pixel,he2017mask}.
\item these somehow still uses some kind of object detector (at least to find the number of objects), but they do not necessary analyse one proposal at the time: use an object detector to enumerate candidate instances and then perform pixel-level segmentation of each instance \cite{liang2018proposal,dai2016instance,li2017fully,liang2016reversible,arnab2017pixelwise} \TODO{check \cite{dai2016instance}}
% \SOURCE{\cite{kong2018recurrent}
\end{itemize}

\item \textbf{Proposal-free methods:} 
\begin{itemize}
\item box-free \cite{pinheiro2015learning,pinheiro2016learning,hu2017fastmask}; joint segmentation and instance labeling in a combinatorial framework \cite{kirillov2017instancecut}; recurrent models \cite{romera2016recurrent,ren2017end}; encode instance relationships to classes and exploit the boundary information  \cite{jin2016object}; sequential framework to gradually group from points to lines and then instances \cite{liu2017sgn}
% \item From end-to-end recurrent attention: \textit{Other approaches us- ing FCNs are proposal-free, but rely on a \textbf{bottom-up merging process}\textbf{}. Liang et al. [26] predict dense pixel prediction of ob- ject location and size, using clustering as a post-processing step. Uhrig et al. [41] present another approach based on FCNs, which is trained to produces a semantic segmen- tation as well as an instance-aware angle map, encoding the instance centroids. Post-processing based on template matching and instance fusion produces the instance identi- ties. Importantly, they also used ground-truth depth labels in training. Concurrent work [2, 19, 22] also explores a similar idea of using FCNs to output instance-sensitive embeddings.}
\item \textbf{Pixel embedding vectors}: 
\begin{itemize}
\item supervised vectors \cite{bai2017deep}, unsupervised vectors  \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic} of which \cite{kong2018recurrent} is trained end-to-end;  using scene depth information \cite{uhrig2016pixel}, \TODO{check \cite{sironi2014multiscale}} 
%    \TODO{more on pose estimation, vector distance transform, deep coloring?, ECCV semi-convolutions}

@@

\item \textbf{Graph clustering related work}:
\begin{itemize}
    \item popular in image segmentation: \textbf{agglomerative clustering}.
    \item Why: more efficient than divisive approaches and graph cuts; does not usually require to specify the final number of clusters (e.g. spectral clustering) or seed nodes (e.g. watershed, random walker) 
    % old graph cut paper: \cite{shi2000normalized}
    % \item \emph{[other clustering methods working in an euclidean embedding space like mean-shift, K-means, Mixture models, BIRCH... can most probably be omitted]}
    \item many segmentation pipelines used to start the agglomeration from superpixels (SLIC, \cite{felzenszwalb2004efficient}, watershed) to reduce size of the problem 
    \item usually we build an hierarchy of clusters (or a \emph{merge-tree}): \TODO{find meaningful order}
    \item clustering paper suggested by Roman

### 2019-04-24 chapters/3_algorithm.tex
Update figures
Updates to intro and algorithm

\begin{minipage}[b]{\textwidth}
        \centering
        \begin{minipage}[b]{0.45\textwidth}
\centering
        \includegraphics[width=\textwidth,trim=0.1in 0.4in 0.2in 0.2in,clip]{./figs/edge_contraction.png} % left bottom right top
\captionof{figure}{\small 
Example of edge contraction: the edge $e_{uv}$ is selected from priority queue; after nodes $u$ and $v$ are merged and $e_{uv}$ is deleted, there are two double edges $e_1$ and $e_2$ left in the graph...  
\label{fig:edge_contraction_and_contr_graph} }
    \end{minipage}\hspace{0.04\textwidth}
    \begin{minipage}[b]{0.45\textwidth}
        \centering
\includegraphics[width=0.8\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/cannot-lin-constraints.png}
\captionof{figure}{\small 
Example of agglomerative clustering on signed graph with and without cannot-link constraints...
\label{fig:algorithm_with_without_CLC}}
    \end{minipage}
\end{minipage}

@@

\subsection{Contracted graph and cannot-link constraints} \label{sec:contr_graph_and_CLC}

\begin{itemize}
\item Define graph formalism and clustering $\Pi$. Make comment about special case of unsigned graph
\item Define multicut and associated energy

\item Given a clustering $\Pi$ and a graph $\mathcal{G}(V,E,W)$, the interaction between two clusters $S_1, S_2 \in \Pi$ is usually defined in terms of a \emph{linkage criterion}, i.e. a function of all the edge weights connecting the two clusters:
\begin{equation} \label{eq:linkage_criterion_def}
\begin{gathered}
\mathcal{L}(S_1,S_2) = \mathcal{L}(\mathcal{W})\quad \\
   \text{where} \quad \mathcal{W} = \{ W(e_{uv})| u\in S_1, v\in S_2 \}.
\end{gathered}
\end{equation}

\item A cannot-link-constraint defines a mutual exclusion relationship between two nodes in the graph and is used to specify that the these two nodes should not be associated with the same cluster. (the alg. will introduce them dynamically)
\item Define contracted graph from given graph  $\mathcal{G}$ and clustering $\Pi$; explain edge contraction shown in Fig. 2 and define \emph{update rule} $f(w_1, w_2)$

>>>>

\begin{minipage}[t]{\textwidth}
        \centering
        \begin{minipage}[t]{0.45\textwidth}
\centering
        \includegraphics[width=\textwidth,trim=0.1in 0.4in 0.2in 0.2in,clip]{./figs/edge_contraction.png} % left bottom right top
\captionof{figure}{\small 
Example of edge contraction: the edge $e_{uv}$ is selected from priority queue; after nodes $u$ and $v$ are merged and $e_{uv}$ is deleted, there are two double edges $e_1$ and $e_2$ left in the graph...  
\label{fig:edge_contraction_and_contr_graph} }
    \end{minipage}\hspace{0.04\textwidth}
    \begin{minipage}[t]{0.45\textwidth}
        \centering
\includegraphics[width=0.8\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/cannot-lin-constraints.jpg}
\captionof{figure}{\small 
Example of agglomerative clustering on signed graph with and without cannot-link constraints...
\label{fig:algorithm_with_without_CLC}}
    \end{minipage}
\end{minipage}

@@

\subsection{Signed graph formalism: edge contraction and cannot-link constraints} \label{sec:contr_graph_and_CLC}

\begin{itemize}
\item \TODO{First define clustering, then weights, costs} We consider the problem of clustering a simple graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates a positive scalar attribute $w_e^+$ to each edge $e \in E$ representing a merge affinity: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that several formalisms defining unsigned weighted graphs associate to each edge a positive scalar that represents a metric or distance on the graph. In these formalisms, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+: E \rightarrow \mathbb{R}^+$.}. On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates a split tendency $w_e^-$ to each edge: the higher this weight, the greater the desire of the incident vertices to be in different clusters.
Graphs that have only positive weights can be seen as special cases of the previously defined graph $\mathcal{G}(V,E,w^+,w^-)$, when $w^-_e=0$ for every $e \in E$.

\item The set $\Pi$ is defined as a partition of the set of nodes $V$ into $K$ subsets if $V = \cup_{i=1}^K S_i $ and $S_i \cap S_j = \emptyset$ for every $i\neq j \in \{1, ..., K\}$. We call a partition $\Pi$ of $V$ a \emph{clustering} if every $S \in \Pi$ induces a connected subgraph (\emph{cluster}) of $\mathcal{G}$.
\item For any clustering $\Pi$ of $\mathcal{G}$, we define as $E^0_\Pi$ the set of edges linking nodes in the same cluster, and as $E_\Pi^1$ the complementary set of edges whose linked nodes belong to distinct clusters:

\begin{align}
E_\Pi^0 &= \{ uv \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \\
E^1_\Pi &= E \setminus E^0_\Pi.
\end{align}

The set of edges $E_\Pi^1$ is known as the \emph{multicut} of $\mathcal{G}$ associated to the clustering $\Pi$. 
\item Often, graphs with both attractive and repulsive edge attributes are described in terms of a cost function $c: E \rightarrow \mathbb{R}$   The NP-hard multicut graph partition problem also called \emph{correlation clustering} \TODO{cits} amounts to finding a graph multicut $E^1_\Pi$ for which the sum of costs $c_e = w^-_e - w^+_e$  
for every edge e
\item Given a clustering $\Pi$ and a graph $\mathcal{G}(V,E,W)$, the interaction between two clusters $S_1, S_2 \in \Pi$ is usually defined in terms of a \emph{linkage criterion}, i.e. a function of all the edge weights connecting the two clusters:
\begin{equation} \label{eq:linkage_criterion_def}
\begin{gathered}
\mathcal{L}(S_1,S_2) = \mathcal{L}(\mathcal{W})\quad \\
   \text{where} \quad \mathcal{W} = \{ W(e_{uv})| u\in S_1, v\in S_2 \}.
\end{gathered}
\end{equation}

\item A cannot-link-constraint defines a mutual exclusion relationship between two nodes in the graph and is used to specify that the these two nodes should not be associated with the same cluster. (the alg. will introduce them dynamically)
\item The algorithm that we will present in the next section iteratively performs a sequence of \emph{edge contractions} on the original graph $\mathcal{G}(V,E,w^+, w^-)$.

\item define \emph{update rule} $f(c_1, c_2)$
